---
title: "IST707_FinalProject_ExearioBoscan"
author: "Exeario Boscan"
date: "3/9/2022"
output: pdf_document
---
```{r}
library(tidyverse)
library(knitr)
library(plyr)
library(dplyr)
library(arules)
library(cluster)
library(factoextra)
library(ClusterR)
library(colorspace)
library(tm)
library(DAAG)
library(party)
library(rpart)
library(rpart.plot)
library(mlbench)
library(caret)
library(pROC)
library(tree)
library(readr)
library(ggplot2)
```

```{r}
Covid19Africa <- read.csv("covid_africa_weekly_trend.csv")
```

```{r}
str(Covid19Africa)
```

```{r}
data.frame(Covid19Africa)
```
```{r}
summary(Covid19Africa)
```


## Classification 
```{r}
rules <- apriori(Covid19Africa,parameter=list(support=0.005, confidence=0.5))
```
```{r}
library(arulesViz)
```





```{r}
rules1 <- apriori(Covid19Africa, parameter = list(supp = 0.001, conf = 0.9, 
                                                 maxlen = 10))
```
```{r}
head(rules1(rules))
``` 
  
  
  
```{r}
library(arulesViz)
```


```{r}
rules2 <- apriori(Covid19Africa,parameter=list(support=0.005, confidence=0.35))
```

```{r}
rules
```
```{r}
inspect(head(rules, n = 3, by = "lift"))
```

```{r}
plot(rules)
```
```{r}
plot(rules1)
```
```{r}
plot(rules2)
```

```{r}
rules3 <- apriori(Covid19Africa, parameter = list(supp = 0.001, conf = 0.9, 
                                                 maxlen = 4))
```
```{r}
plot(rules3)
```













# VARIABLES VISUALIZATION
```{r}
plot(Covid19Africa$Cases.in.the.last.7.days, Covid19Africa$Cases.in.the.preceding.7.days)
```


```{r}
library(purrr)
library(tidyr)
library(ggplot2)

hist(Covid19Africa$Cases.in.the.last.7.days)
hist(Covid19Africa$Cases.in.the.preceding.7.days)
hist(Covid19Africa$Weekly.Case...Change)
hist(Covid19Africa$Cases.in.the.last.7.days.1M.pop)
hist(Covid19Africa$Deaths.in.the.last.7.days)
hist(Covid19Africa$Deaths.in.the.preceding.7.days)
hist(Covid19Africa$Weekly.Death...Change)
hist(Covid19Africa$Deaths.in.the.last.7.days.1M.pop)
hist(Covid19Africa$Population)
```


## NAIVE BAYES
```{r}
library(dplyr)    
library(ggplot2) 
library(caret)    
```

```{r}
features <- setdiff(names(train), "Covid19Africa")
x <- train[, features]
y <- train$Covid19Africa
```



```{r}
trainset <- read.csv("covid_africa_weekly_trend.csv")
trainset$Survived=factor(trainset$Cases.in.the.last.7.days)
trainset$Pclass=ordered(trainset$Cases.in.the.preceding.7.days)
```


```{r}
testset <- read.csv("covid_africa_weekly_trend.csv")
testset$Cases.in.the.last.7.days=factor(testset$Cases.in.the.last.7.days)
testset$Cases.in.the.preceding.7.days=ordered(testset$Cases.in.the.preceding.7.days)
```

```{r}
trainset <- read.csv("covid_africa_weekly_trend.csv")
trainset$Cases.in.the.last.7.days=factor(trainset$Cases.in.the.last.7.days)
trainset$Cases.in.the.preceding.7.days=ordered(trainset$Cases.in.the.preceding.7.days)
```


```{r}
library(e1071)
```

```{r}
nb=naiveBayes(Cases.in.the.last.7.days~., 
              data = trainset, laplace = 1, na.action = na.pass)
```






##Break

```{r}
library(cluster)
library(factoextra)
library(ClusterR)
library(colorspace)
library(tm)
library(tidyverse)
```

#Decision Tree
```{r}
library(tree)
```

```{r}
mydata <- Covid19Africa
```


```{r}
set.seed(1234)
ind <- sample(2, nrow(mydata), replace = T, prob = c(0.5, 0.5))
train <- mydata[ind == 1,]
test <- mydata[ind == 2,]
```

# SECTION 2: Build and Tune Decision Tree Models

## 1. TREE CLASSIFICATION
```{r}
tree <- rpart(no ~., data = train)
rpart.plot(tree)
printcp(tree)
```

## HAC Clustering ##
```{r}
Covid19Africa <- Covid19Africa
Covid19Africa2 <- Covid19Africa[,-5]
species_labels <- Covid19Africa[,5]
library(colorspace) 
species_col <- rev(rainbow_hcl(3))[as.numeric(species_labels)]

d_Covid19Africa <- dist(Covid19Africa2) 
hc_Covid19Africa <- hclust(d_Covid19Africa, method = "complete")
Covid19Africa_Cases.in.the.last.7.days <- rev(levels(Covid19Africa[,5]))

library(dendextend)
dend <- as.dendrogram(hc_Covid19Africa)



dend <- color_branches(dend, k=3) #, groupLabels=iris_species)


labels_colors(dend) <-
  rainbow_hcl(3)[sort_levels_values(
    as.numeric(Covid19Africa[,5])[order.dendrogram(dend)]
  )]


labels(dend) <- paste(as.character(Covid19Africa[,5])[order.dendrogram(dend)],
                      "(",labels(dend),")", 
                      sep = "")

dend <- hang.dendrogram(dend,hang_height=0.1)

dend <- set(dend, "labels_cex", 0.5)
par(mar = c(3,3,3,7))
plot(dend, 
     main = "Clustered Covid19Africa data set
     (10 Variables)", 
     horiz =  TRUE,  nodePar = list(cex = .007))
legend("topleft", legend = Covid19Africa_Cases.in.the.last.7.days, fill = 
         rainbow_hcl(3))
```

## MULTIMODEL

```{r}
trainset <- read.csv("covid_africa_weekly_trend_test.csv")
testset <- read.csv("covid_africa_weekly_trend.train.csv")
```

```{r}
trainset$Cases.in.the.last.7.days=factor(trainset$Cases.in.the.last.7.days)
trainset$Cases.in.the.preceding.7.days=ordered(trainset$Cases.in.the.preceding.7.days)
testset$Cases.in.the.last.7.days=factor(testset$Cases.in.the.last.7.days)
testset$Cases.in.the.preceding.7.days=ordered(testset$Cases.in.the.preceding.7.days)
```




##SVM 

```{r}
install.packages("kernlab")
library(kernlab)
```

```{r}
str(Covid19Africa)
```



```{r}
dim(Covid19Africa)
```

```{r}
table(Covid19Africa$Country.Other)
```


```{r}
randIndex <- sample(1:dim(Covid19Africa)[1])
summary(randIndex)
```

```{r}
length(randIndex)
```

```{r}
head(randIndex)
```

```{r}
cutPoint2_3 <- floor(2 * dim(Covid19Africa)[1]/3)
cutPoint2_3
```

```{r}
trainData <- Covid19Africa[randIndex[1:cutPoint2_3],]
```

```{r}
testData <- Covid19Africa[randIndex[(cutPoint2_3+1):dim(Covid19Africa)[1]],]
```

```{r}
svmOutput <- ksvm(type ~., data=trainData, kernel = 
                    "rbfdot",kpar="automatic",C=5,cross=3, prob.model=TRUE)
svmOutput
```


##Random Forest##
```{r}
library(randomForest)
set.seed(4543)
Covid19Africa.rf <- randomForest(Cases.in.the.last.7.days ~ ., data=Covid19Africa, ntree=100,
keep.forest=FALSE, importance=TRUE)
importance(Covid19Africa.rf)
importance(Covid19Africa.rf, type=1)
```

```{r}
plot(Covid19Africa.rf)
```

```{r}
model<- ctree( ~ ., trainData)
plot(model)
```
## 2 RAMDON FOREST
```{r}
library(rpart)
library(readr)
library(caTools)
library(dplyr)
library(party)
library(partykit)
library(rpart.plot)
```

```{r}
set.seed(123)
sample_data = sample.split(Covid19Africa, SplitRatio = 0.80)
trainData <- subset(Covid19Africa, sample_data == TRUE)
testData <- subset(Covid19Africa, sample_data == FALSE)
```

```{r}
rtree <- rpart(Cases.in.the.preceding.7.days ~ ., trainData)
rpart.plot(rtree)
```


## Multimodel e1071 ###

```{r}
trainset <- read.csv("covid_africa_weekly_trend.csv")
trainset$Cases.in.the.last.7.days=factor(trainset$Cases.in.the.last.7.days)
trainset$Cases.in.the.preceding.7.days=ordered(trainset$Cases.in.the.preceding.7.day)
```

```{r}
testset <- read.csv("covid_africa_weekly_trend.csv")
testset$Cases.in.the.last.7.days=factor(testset$Cases.in.the.last.7.days)
testset$Cases.in.the.preceding.7.days=ordered(testset$Cases.in.the.preceding.7.day)
```

```{r}
myVars=c("Cases.in.the.preceding.7.days","Weekly.Case...Change", 
         "Weekly.Death...Change", "Cases.in.the.last.7.days")
newtrain=trainset[myVars]
newtest=testset[myVars]
```

```{r}
library(e1071)
```

## NAIVE BAYES MODEL with e1071

```{r}
nb=naiveBayes(Cases.in.the.last.7.days~., data = newtrain, laplace = 1, na.action = na.pass)
```

```{r}
pred=predict(nb, newdata=newtest, type=c("class"))
```

```{r}
myids=c("Deaths.in.the.last.7.days")
id_col=testset[myids]
newpred=cbind(id_col, pred)
```

```{r}
colnames(newpred)=c("Deaths.in.the.last.7.days", "Cases.in.the.last.7.days")
```

```{r}
write.csv(newpred, file="covid_africa_weekly_trend-NB-pred.csv",
row.names=FALSE)
```

### Naive Bayes
```{r}
library(caret)
library(DescTools)
library(e1071)
```

```{r}
DM <- read.csv(file = "covid_africa_weekly_trend.csv",
                   stringsAsFactors = FALSE)
```

```{r}
Abstract(DM)
```




```{r}
DM$Cases.in.the.preceding.7.days <- factor(x = DM$Cases.in.the.preceding.7.days,
                    levels = c("Below_Avg", "Above_Avg"))
```

```{r}
plot(x = DM$Cases.in.the.preceding.7.days, main = "Number of Cases")
```

# Preparing Predictor Variables
```{r}
noms <- c("Country.Other")
DM[ ,noms] <- lapply(X = DM[ ,noms],
                     FUN = factor)
```

```{r}
set.seed(831) # initialize the random seed

# Generate the list of observations for the
# train dataframe
sub <- createDataPartition(y = DM_bcs$, 
                           p = 0.80, 
                           list = FALSE)